---
title: "overview"
output: rmarkdown::html_vignette
authors: Lester Carver and Spandan Pandey
vignette: >
  %\VignetteIndexEntry{overview}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r setup}
library(nightlightF22)
library(dplyr)
library(sf)
library(ggplot2)
library(terra)
library(tidyr)
library (knitr)
```

# Introduction



## Project Objectives:
1. Finding whether neighborhoods with public housing more brightly lit than non-public housing in two major US cities (Boston and San Francisco).
2. 
3.


# Approach and Method

## Data:

- The monthly average night lights for 2012 - 2021, averaged for January - March per year and then the long-term average in the time series. This will come from the VNP46A3 - VIIRS BRDF-Adjusted Monthly Nighttime Lights, which is a monthly, 15 arc second raster of nocturnal visible light.
- Building footprints for each study area
- Public housing locations (to be overlayed with building footprints to determine building structure)
- 2020 Gridded population for each study area
- 2020 Census tracts for each study area


## Code:

- Intersect public housing locations with building footprints to get structure of public housing.
- Convert nightlight hdf5 files to geotiff and stack.
- Estimating population based on building volume and gridded population. 
- Calculating the monthly average and long-term average of nightlights.
- Identifying similar areas in terms of building structure and population of non-public housing and public housing. 
- Sample pixels with and without public housing.
- Compare the average and long-term average monthly nighttime radiance using regression analysis.

The necessary libraries include: `terra`, `dplyr`, `tidyr`, `sf`, and `ggplot2`.

For division of work, each teammate will take one of the study areas so will perform all steps, just with different locations.

## Timelines:

```{r, echo = FALSE}
deadline <- read.csv(system.file("data/GEOG346_Timeline_LCSP.csv", package = "nightlightF22" ))
kable(deadline, caption = "Final Project Timeline", col.names = c("Tentative date", "Activity", "Members"))

```


## Anticipated outcomes: 
- We will be able to determine whether areas with public housing are brighter or not by comparing areas with similar populations and urban structure. 
- We expect to be able to discuss the results in relation to whether there are different levels of surveillance between public housing and non-public housing areas (and whether we can detect those differences using nightlight imagery).


