---
title: "overview"
output: rmarkdown::html_vignette
authors: Lester Carver and Spandan Pandey
vignette: >
  %\VignetteIndexEntry{overview}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r setup}
library(nightlightF22)
library(dplyr)
library(sf)
library(ggplot2)
library(terra)
library(tidyr)
library (knitr)
```

# Introduction



## Project Objectives:
1. Finding whether neighborhoods with public housing more brightly lit than non-public housing in two major US cities (Boston and San Francisco).
2. 
3.


# Approach and Method

## Data:

- The monthly average night lights for 2012 - 2021, averaged for January - March per year and then the long-term average in the time series. This will come from the VNP46A3 - VIIRS BRDF-Adjusted Monthly Nighttime Lights, which is a monthly, 15 arc second raster of nocturnal visible light.
- Building footprints for each study area
- Public housing locations (to be overlayed with building footprints to determine building structure)
- 2020 Gridded population for each study area
- 2020 Census tracts for each study area


## Code:

- Intersect public housing locations with building footprints to get structure of public housing.
- Convert nightlight hdf5 files to geotiff and stack.
- Estimating population based on building volume and gridded population. 
- Calculating the monthly average and long-term average of nightlights.
- Identifying similar areas in terms of building structure and population of non-public housing and public housing. 
- Sample pixels with and without public housing.
- Compare the average and long-term average monthly nighttime radiance.

The necessary libraries include: `terra`, `dplyr`, `tidyr`, `sf`, and `ggplot2`.

For division of work, each teammate will take one of the study areas so will perform all steps, just with different locations.

<!-- ## Timelines: Provide a timeline for when each portion of the analysis will be completed. These timelines should be constructed relative to the time period of presentations (during the last two weeks of class) and final project submission (during exam week). For teams, names should be associated with each step on the timeline. -->

```{r, echo = FALSE}
deadline <- read.csv(system.file("data/GEOG346_Timeline_LCSP.csv", package = "nightlightF22" ))
kable(deadline, caption = "Final Project Timeline", col.names = c("Tentative date", "Activity", "Members"))

```




<!-- #Anticipated outcomes: Briefly describe, as bullet points, the outcomes you expect for each of your primary project objectives -->


