---
title: "GEOG346 - Final Project Overview"
output: rmarkdown::html_vignette
author: "Lester Carver and Spandan Pandey"
date: "11-23-2022"
vignette: >
  %\VignetteIndexEntry{overview}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r setup, echo = FALSE}
library(nightlightF22)
library(dplyr)
library(sf)
library(ggplot2)
library(terra)
library(tidyr)
library (knitr)
```

# Introduction

The excessive or poor use of artificial outdoor light in urban and suburban areas has adverse impacts on humans and non-humans.Its contribution to the increase in CO2 in the atmosphere is critical in the context of climate change. Apart from pollution, it is important to study the socioeconomic and political dimensions of the nighttime light exposure due to its increasing use in surveillance by the police.

In this project, we are looking at the extent of nighttime brightness around public housing across two major US cities: Boston and San Francisco.It is an extension of the previous semester's work that used Visible Infrared Imaging Radiometer Suite (VIIRS) nightlights data for a similar comparison for the neighborhoods of New York City. Our aim is to find whether neighborhoods with public housing are more brightly lit than those neighborhoods with non-public housing in two major US cities Boston and San Francisco.

## Project Objectives:
1. To evaluate any correlation between brightly lit neighborhoods and neighborhoods with public housing across two US cities.
2. To assess the feasibility of nightlight imagery to find differences of excessively lit neighborhood and those which are not.
3. To detect any changes in the level of nighttime brightness between 2012 and 2021.
4. To understand the limitations of the available data in the assessment of nighttime light levels and providing suggestions for improvement.


# Approach and Method

## Data:

- The monthly average night lights for 2012 - 2021, averaged for January - March per year and then the long-term average in the time series. This will come from the VNP46A3 - VIIRS BRDF-Adjusted Monthly Nighttime Lights, which is a monthly, 15 arc second raster of nocturnal visible light.
- Building footprints for each study area
- Public housing locations (to be overlayed with building footprints to determine building structure)
- 2020 Gridded population for each study area
- 2020 Census tracts for each study area


## Code:

- Intersect public housing locations with building footprints to get structure of public housing.
- Convert nightlight hdf5 files to geotiff and stack.
- Estimating population based on building volume and gridded population. 
- Calculating the monthly average and long-term average of nightlights.
- Identifying similar areas in terms of building structure and population of non-public housing and public housing. 
- Sample pixels with and without public housing.
- Compare the average and long-term average monthly nighttime radiance using regression analysis.

The necessary libraries include: `terra`, `dplyr`, `tidyr`, `sf`, and `ggplot2`.

For division of work, each teammate will take one of the study areas so will perform all steps, just with different locations.


## Timelines: 

```{r, echo = FALSE}
deadline <- read.csv(system.file("data/GEOG346_Timeline_LCSP.csv", package = "nightlightF22" ))
kable(deadline, caption = "Final Project Timeline", col.names = c("Tentative date", "Activity", "Members"))

```


## Anticipated outcomes: 
- We will be able to determine whether areas with public housing are brighter or not by comparing areas with similar populations and urban structure. 
- We expect to be able to discuss the results in relation to whether there are different levels of surveillance between public housing and non-public housing areas (and whether we can detect those differences using nightlight imagery).


